\pkg{partykit}: A Toolkit for Recursive Partytioning

### 2010-04-22 pkg/inst/doc/introduction.Rnw
some checks
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@165 255f4249-2263-4417-b1ea-8498779e27a7

<<party-1, echo = TRUE>>=
t1 <- party(n1, 
   data = data.frame(iris, 
       "(fitted)" = fitted_node(n1, data = iris),
       "(response)" = iris$Species))
@

@@

This strategy can be implemented based on the data (response and features) and 
some case weights as follows:
<<mytree-1, echo = TRUE>>=
findsplit <- function(response, data, weights) {

@@

Now we have to set-up the recursion for growing a recursive 
\code{partynode} structure:
<<mytree-2, echo = TRUE>>=
growtree <- function(id = 1L, response, data, weights) {

@@

    ### name of the response variable
    response <- all.vars(formula)[1]
    ### data without missing values, response comes last
    data <- data[complete.cases(data), 
                 c(all.vars(formula)[-1], response)]
    if (is.null(weights)) weights <- rep(1, nrow(data))

>>>>

<<party-1, echo = TRUE>>=
t1 <- party(n1, 
   data = iris,
   fitted = data.frame("(fitted)" = fitted_node(n1, data = iris),
                       "(response)" = iris$Species,
                       check.names = FALSE))
t1
@

@@

This strategy can be implemented based on the data (response and features) and 
some case weights as follows (\code{response} is just the name of the response
and \code{data} is a data frame with all variables):
<<mytree-1, echo = TRUE>>=
findsplit <- function(response, data, weights) {

@@

In order to actually grow a tree on data, 
we have to set-up the recursion for growing a recursive 
\code{partynode} structure:
<<mytree-2, echo = TRUE>>=
growtree <- function(id = 1L, response, data, weights) {

@@

    ### name of the response variable
    response <- all.vars(formula)[1]
    ### data without missing values, response comes last
    data <- data[complete.cases(data), 
                 c(all.vars(formula)[-1], response)]
    ### data is numeric
    stopifnot(all(sapply(data, is.numeric)))

    if (is.null(weights)) weights <- rep(1, nrow(data))
    ### weights are case weights, i.e., integers
    stopifnot(length(weights) == nrow(data) &
              max(abs(weights - floor(weights))) < .Machine$double.eps)
